Ceph Parallel File System Evaluation Report

### 2013-08-28 introduction.tex
fixed ORNL TOP500 footnote

Oak Ridge Leadership Computing Facility (OLCF) at Oak Ridge National Laboratory
(ORNL) has a long history of deploying and running very-large-scale
high-performance computing (HPC) systems~\cite{top500-ornl}. The facility
hosted the Jaguar supercomputer up until recently, which was upgraded to the
Titan supercomputer. In order to satisfy the I/O demand of such supercomputers
(as well as, other OLCF computational, analysis, and visualization clusters),
OLCF also hosts large-scale file and storage systems. Lustre has been OLCF's
choice as the distributed parallel file system.  The latest incarnation of such
large-scale file systems hosted at OLCF is Spider II\cite{spider2}. Spider II
is the forklift-upgrade of its predecessor, Spider, which was deployed in 2008.
Spider II, deployed in 20013, is designed to operate at over 1 TB/s peak
aggregate I/O throughput and has a 40 PB of raw disk capacity. As the scratch
file system connected to a leadership computing platform at the scale of Titan,
Spider II emphasizes \textit{capability} over \textit{capacity}. However, we
also recognize that there are a wide variety of scientific data and workloads
with different performance and data access requirements (e.g., RESTful
interface, S3-like API, cloud solution integration) which might not be
efficiently serviced by Lustre. OLCF is constantly evaluating new and emerging
file and storage system technologies.

>>>>

Oak Ridge Leadership Computing Facility (OLCF) at Oak Ridge National Laboratory
(ORNL) has a long history of deploying and running very-large-scale
high-performance computing (HPC)
systems~\footnote{\url{http://www.top500.org/site/48553}}. The facility hosted
the Jaguar supercomputer up until recently, which was upgraded to the Titan
supercomputer. In order to satisfy the I/O demand of such supercomputers (as
well as, other OLCF computational, analysis, and visualization clusters), OLCF
also hosts large-scale file and storage systems. Lustre has been OLCF's choice
as the distributed parallel file system.  The latest incarnation of such
large-scale file systems hosted at OLCF is Spider II\cite{spider2}. Spider II
is the forklift-upgrade of its predecessor, Spider, which was deployed in 2008.
Spider II, deployed in 20013, is designed to operate at over 1 TB/s peak
aggregate I/O throughput and has a 40 PB of raw disk capacity. As the scratch
file system connected to a leadership computing platform at the scale of Titan,
Spider II emphasizes \textit{capability} over \textit{capacity}. However, we
also recognize that there are a wide variety of scientific data and workloads
with different performance and data access requirements (e.g., RESTful
interface, S3-like API, cloud solution integration) which might not be
efficiently serviced by Lustre. OLCF is constantly evaluating new and emerging
file and storage system technologies.
